\vspace{-3em} \includegraphics[width=.1\textwidth]{Figures/logo.png} \\ \includegraphics[width=4cm]{Figures/logotext.png} \\

### 2014-10-06 report/article_4.tex
writeup devel

I analysed the {\bf London house prices} dataset is several innovative
ways. Firstly \emph{fractal context} shows how house sales within an
arbitrary area relate to those if neighbouring districs, up and down
the postcode hierarchy. Secondly, I fit \emph{ARIMA models} to
forecast an area's price trend into the future, with an eye to
suggesting profitable investments. Finally, these and other metrics
were combined into an \emph{investment grade} for a given postcode
area. Combined this set of analyses forms the basis of \logo, a
product aimed at ``democratising real estate investment'', offering
individuals and businesses quantitative real estate insights for
data-driven investment decisions.

@@

%----------------------------------------------------------------------------------------
%	METHODS
%----------------------------------------------------------------------------------------
\clearpage
\section*{Value generation}

\subsection*{Socio-economic value}

\subsection*{Initial product}
\logo \hspace{.1em} would first be released as both a web service and
associated apps for mobiles and tablets. These would offer limited
analysis and visualisation for free, with user analytics and feedback
helping to validate the business model.

\begin{wrapfigure}{r}{.4\textwidth}
\begin{center}
\includegraphics[width=.39\textwidth]{Figures/mockup.png}
\caption{ iOS app mock-up.}
\end{center}
\end{wrapfigure}

@@

Additionally the business could pivot to an analytics provider for
existing letting and sales sites, offering unique data insights
indirectly to the consumer market, or as independent fund consultants
for the financial services. Having produced a first-to-market
innovative product positions \logo \hspace{.1em} to succeed as a
provider of advanced real estate investment analytics. \\

\begin{figure}[h!]
\begin{center}
\includegraphics[width=.1\textwidth]{Figures/logo.png} \\
\includegraphics[scale=.12]{Figures/logotext.png} \\
\caption*{ {\sf Democratising real estate investment}}
\end{center}
\end{figure}

\subsection*{Business development}

>>>>

I analysed the {\bf London house prices} dataset is several innovative
ways. Firstly \emph{fractal context} shows how house sales within an
arbitrary area relate to those if neighbouring districs, up and down
the postcode hierarchy. Secondly, I fit \emph{ARIMA models} to
forecast an area's price trend into the future, with an eye to
suggesting profitable investments. Finally, these and other metrics
were combined into an \emph{investment grade} for a given postcode
area. Combined this set of analyses forms the basis of \logo, a
startup aimed at ``democratising real estate investment'', offering
individuals and businesses quantitative real estate insights for
data-driven investment decisions.

@@

%----------------------------------------------------------------------------------------
%	METHODS
%----------------------------------------------------------------------------------------
%\clearpage
\section*{Value generation}

The above-described analyses form the basis of \logo\hspace{.1em}, a
start-up aimed at ``democratising real estate investment'' by
making deep-dive analytics data available both to a consumer and
professional investment market.

\subsection*{1. Analytics provider for online house sales and lettings
agents}

\logo\hspace{.1em} can provide {\bf real-time property area analytics} to
existing market leaders in {\bf online sales and lettings}.

\begin{wrapfigure}{l}{.2\textwidth}
\begin{center}
\includegraphics[width=.15\textwidth]{Figures/zoopla.png}
\includegraphics[width=.2\textwidth]{Figures/rightmove.jpg}
\caption*{ Example customer segments.}
\end{center}
\end{wrapfigure}

There are currently no mainsteam property sales or rental sites that
attempts to provide any quantitative insights to contextualise a
property's list price. Some list recent nearby sales in plain text,
but the wealth of historical sales data available allows for much
richer displays (as demonstrated with the fractal context view,
\emph{above}), which offer valuable and practical insights to
prospective homebuyers.

This added feature would help differentiate a given sales and letting
site as well as increase the brand positioning of \logo\hspace{.1em}
within the real estate sector. Contextual maps could be drawn as
interactive D3.js visualisations and neatly integrated with a typical
property search. Additionally, web analytics data from our partnered
site could be fed-back to help further enhancement and expansion of
the data-driven insights and visualisations we offer.

\subsection*{2. Direct-to-consumer demo application}
\logo \hspace{.1em} would release both a {\bf web service} and associated
{\bf mobiles and tablet applications}. These would offer limited analysis and
visualisation without any fee, with collected user data and feedback helping to
validate the business model and develop our software.

\begin{wrapfigure}{r}{.4\textwidth}
\begin{center}
\includegraphics[width=.39\textwidth]{Figures/mockup.png}
\caption{ iOS app mock-up.}
\vspace{-2em}
\end{center}
\end{wrapfigure}

@@

\subsection*{3. Real estate data science consultancy}

Having established a property area analytics brand, \logo\hspace{.1em}
will look to develop business relationships with real estate
investment funds and high net-worth individuals as a data-driven
propert investment consultancy and independent analyst for the
financial services. Our domain expertise and existing partnerships and
products would place us as a market leader in this undeveloped segment.

% \begin{figure}[h!]
% \begin{center}
% \includegraphics[width=.1\textwidth]{Figures/logo.png} \\
% \includegraphics[scale=.12]{Figures/logotext.png} \\
% \caption*{ {\sf Democratising real estate investment}}
% \end{center}
% \end{figure}
